MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-04-24 Manuscript/Manuscript-2.Rmd
vsn 2

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$Kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. Here, maximum likelihood is used to fit the data to the phylogeny under a Brownian motion model of evolution. A parameter ($\lambda$) is included, which transforms the lengths of the internal branches of the phylogeny to improve the fit [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$, which ranges from $0\to1$, is then treated as a measure of phylogenetic signal; with values close to 0 signifying little phylogenetic signal, and values close to 1 indicating that trait variation accumulates according to Brownian motion. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic regression  (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

Evolutionary biologists commonly seek to describe the relative strength of phylogenetic signal in phenotypic traits, to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. This is often accomplished by interpreting empirical estimates of $\lambda$; with $\lambda\approx0$ signifying 'weak' phylogenetic signal, and $\lambda\approx1$ being interpreted as 'strong' phylogenetic signal [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Other approaches for interpreting $\lambda$ are more statistical, through the use of confidence intervals [@Vandelook2019] or likelihood ratio tests that compare the observed model fit to that obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019]. Likewise, qualitative comparisons of $\lambda$ across multiple phenotypic traits have also been used to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019]. Indeed, it seems intuitive to interpret the strength of phylogenetic signal in this manner, as $\lambda$ is a parameter on a bounded scale ($0\to1$) for which interpretation of its extremal points are well known ($\lambda=0$ is no phylogenetic signal, while $\lambda=1$ corresponds to Brownian motion). However, equating values of $\lambda$ directly to the strength of phylogenetic signal presumes two important statistical properties that have not been fully explored. \hfill\break

First, it presumes that values of $\lambda$ can be precisely estimated, and that parameter estimates of $\lambda$ are representative of the underlying phylogenetic signal. However, for such applications, understanding the precision in estimating levels of phylogenetic signal is paramount, because biological inferences regarding the strength of phylogenetic signal in phenotypic datasets requires high precision of its estimation. One study [@Boettiger_et_al2012] found that estimates of Pagel's $\lambda$ displayed less variation (i.e., greater precision) when data were simulated on a large phylogeny ($N=281$) as compared to a small one ($N=13$). From this observation it was concluded that insufficient data (i.e., the number of species) was the underlying cause of the increased variation across parameter estimates [@Boettiger_et_al2012]. Indeed, such a pattern is common with statistical estimators, as summary statistics and parameters are often more precise with greater sample sizes [@Cohen1988]. However, this conclusion also assumes that the precision in estimating $\lambda$ remains constant across its range ($\lambda = 0 \to 1$); an assumption that to date, has not been verified. Thus, despite widespread use of Pagel's [-@Pagel1999] $\lambda$ in macroevolutionary studies, at present, we still lack a general understanding of the precision with which $\lambda$ can estimate levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while $\lambda$ is observed on a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets [e.g., meta-analysis: @HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared across datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunatley, not all statistical parameters and test statistics are effect sizes, and thus many summary measures must first be converted to standardized units (i.e., an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. For the case of $\lambda$, this has not yet been explored.  \hfill\break

@@

-Lambda is not precise: holds in estimates, and PGLSregression
  -Precision varies with N (duh) but also WITH INPUT!
  -same input on different N, different lambda.est
  -same lambda.est from different input
  -Boettiger example: add small tips, greatly change lambda...
-Conclusion: Lambda does not quantify strength of phylogenetic signal as is often assumed

@@

-A proposed Effect size for the strength of physig
  -Derivation of effect size (expand on Adams and Collyer 2019 suggestion that an effect size for phylogenetic signal is needed. The ‘gold standard’ of these is a standaredized effect size: (following the meta-analytic literature beginning with Glass 1976).  In other words, a Z-score. So, how does Z work when based on lambda? On kappa?
  - Z-score. could be Lambda or Kappa.  Show it is Kappa
-Comparing the strength of physig
  - two sample Z-score

@@

## $\lambda$ is not Precise

## Lambda does not measure phylogenetic signal

## An effect size for Physig

# Materials and Methods

We conducted a series of computer simulations to evaluate the ability of Pagel's $\lambda$ to estimate known levels of phylogenetic signal. Our primary simulations were based on pure-birth phylogenies; however, we also evaluated patterns on both balanced and pectinate trees to determine whether tree shape affected our findings (see Supporting Information). Our first set of simulations evaluated the extent to which values of $\lambda$ estimated from the data corresponded with actual input levels of phylogenetic signal. For these simulations we generated 50 pure-birth phylogenies at each of six different tree sizes, ranging from 32 to 1024 taxa ($n=2^5 - 2^{10}$). Next, we rescaled the simulated phylogenies by multiplying the internal branches by $\lambda$. We used a set of values that encompassed the entire range of $\lambda$: ($\lambda_{in} = 0.0 \to 1.0$; in 21 intervals of 0.05 units), resulting in 1050 scaled phylogenies at each level of species richness ($n$). Continuous traits were then simulated on each phylogeny under a Brownian motion model of evolution to obtain datasets with known and differing levels of phylogenetic signal. These varied from datasets with no phylogenetic signal (when $\lambda_{in} =0$) to datsets with phylogenetic signal corresponding to what was expected under Brownian motion (when $\lambda_{in} =1$). \hfill\break

Using the simulated phylogenies we estimated the phylogenetic signal in each dataset using Pagel's $\lambda$. Next, for the 1050 datasets at each level of species richness ($n$), we assessed the relationship between $\lambda_{in}$ and $\lambda_{est}$ using regression. Additionally, the precision of $\lambda$ was approximated by observing the variation of $\lambda_{est}$ obtained at each input level of phylogenetic signal ($\lambda_{in}$). Finally, for comparison we characterized the strength of phylogenetic signal in each dataset using a standardized effect size [$Z_K$: sensu @AdamsCollyer2016; @AdamsCollyer2019b] based on $Kappa$. As suggested by Adams and Collyer [-@AdamsCollyer2019], an effect size for phylogenetic signal may be estimated as: $Z_K=\frac{K_{obs}-\mu_K}{\sigma_K}$, where $K_{obs}$ was the observed $Kappa$, and $\mu_K$ and $\sigma_K$ were the mean and standard deviation of the empirical sampling distribution of values obtained from the permutation distribution. $Z_K$ describes the strength of phylogenetic signal as a standard deviate from its sampling distribution, and thus directly measures the strength of signal in a manner that is comparable across datasets. Variation in the set of $Z_K$ at each input level of phylogenetic signal was then calculated as an estimate of precision in $Z_K$. However, because $Z_K$ differs in scale from $\lambda$, we used a linear normalization to standardize $Z_K$ to a uniform distribution ($0\rightarrow1$), and estimated the precision of $Z_K$ from the normalized values. \hfill\break

Our second set of simulations evaluated the extent to which values of $\lambda$ estimated in PGLS regression and ANOVA (i.e., $Y\sim{X}$) corresponded with actual input levels of phylogenetic signal in the response variable. As before we generated 50 pure-birth phylogenies at each of six levels of species richness ($n=2^5 - 2^{10}$), and rescaled each with a set of input $\lambda$ values ($\lambda_{in} = 0.0 - 1.0$; in 21 intervals of 0.05 units). Next, an independent variable $X$ was simulated on each phylogeny under a Brownian motion model of evolution (for PGLS regression). For phylogenetic ANOVA, random groups ($X$) were obtained by simulating a discrete (binary) character on each phylogeny. Next, the dependent variable was simulated in such a manner as to contain a known relationship with $X$ plus random error containing phylogenetic signal. This was accomplished as: $Y=\beta{X}+\epsilon$. Here, the association between $Y$ and $X$  was modeled using a range of values: $\beta=(0.0,0.25, 0.5, 0.75,1.0)$, and the residual error was modeled to contain phylogenetic signal simulated under a Brownian motion model of evolution: $\epsilon=\mathcal{N}(\mu=0,\sigma=\mathbf{C})$: [see @Revell2010 for a similar simulation design]. For each dataset, the fit of the phylogenetic regression was estimated using maximum likelihood, and parameter estimates ($\beta_{est}$ and $\lambda_{est}$) were obtained and evaluated as above. All analyses were performed in R v3.6.0 [@RCT] using the packages `geiger` [@Harmon2008], `caper` [@Orme2013], `phytools` [@Revell2012], and `geomorph` [@AdamsOtarola2013; @AdamsGeomorph]. R-scripts are found in the Supporting Information.

@@

Our first set of simulations revealed several patterns. First, the relationship between $\lambda_{est}$ and $\lambda_{in}$ across the range input levels of phylogenetic signal was $\beta\sim1.0$; indicating that the average $\lambda_{est}$ across datasets for a given simulation condition correctly reflected the input levels of phylogenetic signal. However, as shown in Figure 1, the precision of those estimates varied widely, and in several interesting ways. Predictably, precision was worse at low levels of species richness, where in many cases the set of $\lambda_{est}$ spanned nearly the entire range of possible values (e.g., $n=32$; $\lambda_{in}=0.5$: range of $\lambda_{est}= 0.0\to 0.985$). Second, as species richness increased, variation across estimates of $\lambda$ decreased (Figure 1). This confirmed the pattern identified by Boettiger et al. [-@Boettiger_et_al2012] on  a small ($n=13$) versus a large ($n=281$) phylogeny, and demonstrated that the trend of increasing precision with higher species richness was general; adhering to parametric statistical theory. Importantly however, our broader set of simulations revealed that the precision of $\lambda_{est}$ was not uniform across all levels of phylogenetic signal. Specifically, we found that variation in $\lambda_{est}$ was highest at intermediate levels of phylogenetic signal, and decreased at both lower and higher levels of input signal (Figure 1). This implied that the precision in estimating $\lambda$ was worse at intermediate values, and improved as the levels of phylogenetic signal were closer to $\lambda_{in}=0$ (no phylogenetic signal) or $\lambda_{in}=1$ (Brownian motion). Notably, even at large levels of species richness, the range of $\lambda_{est}$ still encompassed a substantial portion of possible values (e.g., $n=512$; $\lambda_{in}=0.5$: range of $\lambda_{est} = 0.32\to 0.68$). Likewise, the same $\lambda_{est}$ could be obtained from datasets containing vastly different input levels of phylogenetic signal (e.g., $n=512$; $\lambda_{est} = 0.5$; range of $\lambda_{in} = 0.25 \to 0.65$). Taken together, these findings reveal that $\lambda_{est}$ does not precisely characterize observed levels of phylogenetic signal in phenotypic datasets, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ may be highly inaccurate. \hfill\break

@@

When $\lambda$ was incorporated in PGLS regression and ANOVA (i.e., $Y\sim{X}$), we found much the same pattern as in our earlier simulations. Namely, the precision of $\lambda_{est}$ covaried with species richness; where greater precision was obtained at higher levels of species richness (Figure 3). Likewise, the precision in estimating $\lambda$ was worse at intermediate values (Figure 3), and improved as the levels of phylogenetic signal were closer to $\lambda_{in}=0$ (no phylogenetic signal) or $\lambda_{in}=1$ (Brownian motion). Generally, the spread of estimates was slightly broader when $\lambda$  was co-estimated with regression parameters in PGLS regression (Figure 3), as compared to when $\lambda$ was estimated for only the dependent variable (Figure 1). Finally, we found that regression parameters ($\beta$) were accurately estimated when $\lambda$ was included during phylogenetic regression; a result which confirmed earlier findings of Revell [-@Revell2010] (see Supporting Information). \hfill\break

[insert Figure 3 here]

@@

\textbf{Figure 2}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.    \hfill\break

\textbf{Figure 3}. Precision of Pagel's $\lambda$ when incorporated in phylogenetic regression ($|Y\sim X$), across known levels of input phylogenetic signal ($\lambda_{in}$) on phylogenies of various sizes. As phylogenies increase in size, variation in $\lambda_{in}$ decreases; however the precision is not constant across the range of input levels ($\lambda_{in}: 0 \to 1$), and is highest at intermediate levels of phylogenetic signal. \hfill\break

@@

\singlespacing \textbf{Figure 2}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.

@@

\singlespacing \textbf{Figure 3}. Precision of Pagel's $\lambda$ when incorporated in phylogenetic regression ($|Y\sim X$), across known levels of input phylogenetic signal ($\lambda_{in}$) on phylogenies of various sizes. As phylogenies increase in size, variation in $\lambda_{in}$ decreases; however the precision is not constant across the range of input levels ($\lambda_{in}: 0 \to 1$), and is highest at intermediate levels of phylogenetic signal.

>>>>

Several analytical tools have been developed to quantify phylogenetic signal in phenotypic datasets, including measures of serial independence [$\mathbf{C}$: @Abouheif1999], autocorrelation estimates [$I$: @Gittleman1990], statistical ratios of trait variation relative to what is expected given the phylogeny [$Kappa$: @Blomberg_et_al2003; @Adams2014a], and scaling parameters used in maximum likelihood fitting of the data to the phylogeny [$\lambda$: @Pagel1999], among others [e.g., @Klingenberg2010]. The statistical properties of these methods -- namely type I error rates and power -- have also been investigated to determine when phylogenetic signal can be detected and under what conditions [e.g., @Munkemuller_et_al2012; @Pavoine2012;  @DinizFilho2012; @Adams2014a; @MolinaVenegas2017; see also @Revell_et_al2008; @Revell2010]. One of the most widely used methods for characterizing phylogenetic signal in macroevolutionary studies is Pagel's $\lambda$ [@Pagel1999]. Here, maximum likelihood is used to fit the data to the phylogeny under a Brownian motion model of evolution. A parameter ($\lambda$) is included, which transforms the lengths of the internal branches of the phylogeny to improve the fit [@Pagel1999; @Freckleton_et_al2002]. Pagel's $\lambda$ ranges from $0\to1$, with larger values signifying a greater dependence of observed trait variation on the phylogeny. Pagel's $\lambda$ also has the appeal that it may be included in phylogenetic regression  (PGLS) to account for the degree of phylogenetic signal in comparative analyses [see @Freckleton_et_al2002]. \hfill\break

Evolutionary biologists commonly seek to describe the relative strength of phylogenetic signal in phenotypic traits, to determine the extent to which shared evolutionary history has influenced trait covariation among taxa. This is often accomplished by interpreting empirical estimates of $\lambda$; with smaller values signifying 'weak' phylogenetic signal, while larger values are interpreted as 'strong' phylogenetic signal [e.g., @DeMeester2019; @Pintanel2019;@Su2019]. Other approaches for interpreting $\lambda$ are more statistical, through the use of confidence intervals [@Vandelook2019] or likelihood ratio tests that compare the observed model fit to that obtained when $\lambda=0$ or $\lambda=1$ [@Freckleton_et_al2002; @Cooper2010; @Bose2019]. Likewise, qualitative comparisons of $\lambda$ across multiple phenotypic traits have also been used to infer whether the strength of phylogenetic signal is greater in one trait as compared to another [e.g., @Liu2019; @Bai2019]. Indeed, it seems intuitive to interpret the strength of phylogenetic signal in this manner, as $\lambda$ is a parameter on a bounded scale ($0\to1$) for which interpretation of its extremal points are understood ($\lambda=0$ represents no phylogenetic signal, while $\lambda=1$ is phylogenetic signal as expected under Brownian motion). However, equating values of $\lambda$ directly to the strength of phylogenetic signal presumes two important statistical properties that have not been fully explored. \hfill\break

First, it presumes that values of $\lambda$ can be precisely estimated, as biological inferences regarding the strength of phylogenetic signal depend on high accuracy in its estimation. Therefore, understanding the precision in estimating $\lambda$ is paramount. One study [@Boettiger_et_al2012] found that estimates of Pagel's $\lambda$ displayed less variation (i.e., greater precision) when data were simulated on a large phylogeny ($N=281$) as compared to a small one ($N=13$). From this observation it was concluded that insufficient data (i.e., the number of species) was the underlying cause of the increased variation across parameter estimates [@Boettiger_et_al2012]. Indeed, such a pattern is common with statistical estimators, as summary statistics and parameters are often more precise with greater sample sizes [@Cohen1988]. However, this conclusion also assumes that the precision in estimating $\lambda$ remains constant across its range ($\lambda = 0 \to 1$); an assumption that to date, has not been verified. Thus, despite widespread use of Pagel's [-@Pagel1999] $\lambda$ in macroevolutionary studies, at present, we still lack a general understanding of the precision with which $\lambda$ can estimate levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while estimates of $\lambda$ are within a bounded scale ($0\to1$), this does not *de-facto* imply that the estimated values of this parameter correspond to the actual strength of the underlying input signal in the data. For this to be the case, $\lambda$ must be a statistical effect size. Effect sizes are a measure the magnitude of a statistical effect in data, represented on a common scale [@Glass1976; @Cohen1988]. Effect sizes have widespread use in many areas of the quantiative sciences, as they represent measures that may be readily summarized across datasets [e.g., meta-analysis: @HedgesOlkin1985; @Glass1976; @Arnqvist1995], or compared across datasets [e.g., @AdamsCollyer2016; @AdamsCollyer2019b]. Unfortunatley, not all model parameters and test statistics are effect sizes, and thus many summary measures must first be converted to standardized units (i.e., an effect size) for meaningful comparison [see @Rosenthal1994]. As a consequence, it follows that only if $\lambda$ is a statistical effect size can comparisons of estimates across datasets be interpretable. For the case of $\lambda$, this has not yet been explored.  \hfill\break

@@

## The Precision of $\lambda$ is Variable

We conducted a series of computer simulations to evaluate the precision of Pagel's $\lambda$. Our primary simulations were based on pure-birth phylogenies; however, we also evaluated patterns on both balanced and pectinate trees to determine whether tree shape affected our findings (see Supporting Information). First we generated 50 pure-birth phylogenies at each of six different tree sizes, ranging from 32 to 1024 taxa ($n=2^5 - 2^{10}$). Next, we rescaled the simulated phylogenies by multiplying the internal branches by $\lambda_{in} = 0.0 \to 1.0$ using 21 intervals of 0.05 units, resulting in 1050 scaled phylogenies at each level of species richness ($n$). Continuous traits were then simulated on each phylogeny under a Brownian motion model of evolution to obtain datasets with differing levels of phylogenetic signal, that ranged from no phylogenetic signal (when $\lambda_{in} =0$), to phylogenetic signal corresponding reflecting Brownian motion (when $\lambda_{in} =1$). We then calculated the precision (variance: $\sigma^2_\lambda$) of $\lambda$ at each input level of phylogenetic signal and at each level of species richness ($n$). \hfill\break

We also evaluated the precision of $\lambda$ when estimated in PGLS regression and ANOVA (i.e., $Y\sim{X}$). Here, an independent variable $X$ was simulated on each phylogeny under a Brownian motion model of evolution (for PGLS regression). For phylogenetic ANOVA, random groups ($X$) were obtained by simulating a discrete (binary) character on each phylogeny. Next, the dependent variable was simulated in such a manner as to contain a known relationship with $X$ plus random error containing phylogenetic signal. This was accomplished as: $Y=\beta{X}+\epsilon$. Here, the association between $Y$ and $X$  was modeled using a range of values: $\beta=(0.0,0.25, 0.5, 0.75,1.0)$, and the residual error was modeled to contain phylogenetic signal simulated under a Brownian motion model of evolution: $\epsilon=\mathcal{N}(\mu=0,\sigma=\mathbf{C})$: [see @Revell2010 for a similar simulation design]. The fit of the phylogenetic regression was estimated using maximum likelihood, and parameter estimates ($\beta_{est}$ and $\lambda_{est}$) were obtained. Precision estimates ($\sigma^2_\lambda$) at each input level of phylogenetic signal and at each level of species richness ($n$) were then observed. All analyses were performed in R v3.6.0 [@RCT] using the packages `geiger` [@Harmon2008], `caper` [@Orme2013], `phytools` [@Revell2012], and `geomorph` [@AdamsOtarola2013; @AdamsGeomorph]. R-scripts are found in the Supporting Information. \hfill\break

*Results.* We found that the precision of $\lambda_{est}$ varied widely across simulation conditions. Predictably, precision improved as the number of species increased (Figure 1). This confirmed earlier findings of Boettiger et al. [-@Boettiger_et_al2012], and adhered to parametric statistical theory. However, in many cases the set of $\lambda_{est}$ spanned nearly the entire range of possible values (e.g., $n=32$; $\lambda_{in}=0.5$: $\lambda_{est}= 0.0\to 0.985$), revealing that estimates of $\lambda$ were not a reliable indicator of input phylogenetic signal. Importantly, the precision of $\lambda_{est}$ was not uniform across all levels of phylogenetic signal, with the worst precision at intermediate levels of signal ($\lambda_{in}\approx0.5$), and improved precision as input levels approaches 0 and 1 (i.e., $\lambda_{in}\rightarrow0$ & $\lambda_{in}\rightarrow1$). Thus, estimates of $\lambda$ were least reflective of the true input signal at intermediate values. Additionally, even at large levels of species richness, we found that the range of $\lambda_{est}$ still encompassed a substantial portion of possible values (e.g., $n=512$; $\lambda_{in}=0.5$: $\lambda_{est} = 0.32\to 0.68$). Likewise, the same $\lambda_{est}$ could be obtained from datasets containing vastly different input levels of phylogenetic signal (e.g., $n=512$; $\lambda_{est} = 0.5$; $\lambda_{in} = 0.25 \to 0.65$). Results were similar when $\lambda$ was co-estimated with regression parameters in PGLS regression (Figure 2). Here, regression parameters ($\beta$) were accurately estimated, confirming earlier findings of Revell 2010 [-@Revell2010] (see Supporting Information). However, estimates of phylogenetic signal were not, and the spread of $\lambda_{est}$ was even broader tham that observed when $\lambda$ was estimated for only the dependent variable. Taken together, these findings reveal that $\lambda_{est}$ does not precisely characterize observed levels of phylogenetic signal in phenotypic datasets, and that biological interpretations of the strength of phylogenetic signal based on $\lambda$ may be highly inaccurate. \hfill\break

The above findings have several important implications for empirical studies.

@@

## A Standardized Effect Size for Phylogenetic Signal

  -Derivation of effect size (expand on Adams and Collyer 2019 suggestion that an effect size for phylogenetic signal is needed. The ‘gold standard’ of these is a standaredized effect size: (following the meta-analytic literature beginning with Glass 1976).  In other words, a Z-score. So, how does Z work when based on lambda? On kappa?
  - Z-score. could be Lambda or Kappa.  Show it is Kappa
-Comparing the strength of physig
  - two sample Z-score

@@

Finally, for comparison we characterized the strength of phylogenetic signal in each dataset using a standardized effect size [$Z_K$: sensu @AdamsCollyer2016; @AdamsCollyer2019b] based on $Kappa$. As suggested by Adams and Collyer [-@AdamsCollyer2019], an effect size for phylogenetic signal may be estimated as: $Z_K=\frac{K_{obs}-\mu_K}{\sigma_K}$, where $K_{obs}$ was the observed $Kappa$, and $\mu_K$ and $\sigma_K$ were the mean and standard deviation of the empirical sampling distribution of values obtained from the permutation distribution. $Z_K$ describes the strength of phylogenetic signal as a standard deviate from its sampling distribution, and thus directly measures the strength of signal in a manner that is comparable across datasets. Variation in the set of $Z_K$ at each input level of phylogenetic signal was then calculated as an estimate of precision in $Z_K$. However, because $Z_K$ differs in scale from $\lambda$, we used a linear normalization to standardize $Z_K$ to a uniform distribution ($0\rightarrow1$), and estimated the precision of $Z_K$ from the normalized values. \hfill\break

@@

@@

@@

\textbf{Figure 2}. Precision of Pagel's $\lambda$ when incorporated in phylogenetic regression ($Y\sim X$), across known levels of input phylogenetic signal ($\lambda_{in}$) on phylogenies of various sizes. As phylogenies increase in size, variation in $\lambda_{in}$ decreases; however the precision is not constant across the range of input levels ($\lambda_{in}: 0 \to 1$), and is highest at intermediate levels of phylogenetic signal. \hfill\break

\textbf{Figure 3}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.    \hfill\break

@@

\singlespacing \textbf{Figure 2}. Precision of Pagel's $\lambda$ when incorporated in phylogenetic regression ($Y\sim X$), across known levels of input phylogenetic signal ($\lambda_{in}$) on phylogenies of various sizes. As phylogenies increase in size, variation in $\lambda_{in}$ decreases; however the precision is not constant across the range of input levels ($\lambda_{in}: 0 \to 1$), and is highest at intermediate levels of phylogenetic signal.

@@

\singlespacing \textbf{Figure 3}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.
